Flaring star-planet interactions in Kepler and TESS

### 2023-05-19 src/tex/ms.tex
[showyourwork] overleaf sync

Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb$. In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent. This may be an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.

>>>>

Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$. In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent. This may be an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.
